---
output: 
  xaringan::moon_reader:
    css: ["default", "css/xaringan-themer.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "3:2"
    seal: false  
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, fig.width=8, fig.height=6, fig.retina = 3, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(psych)
library(trySimulation)
library(glue)
# library(xaringan)

# theme_set(theme_roboto())

# https://arm.rbind.io/slides/xaringan.html#120

root <- rprojroot::find_rstudio_root_file()
report_path <- file.path(root, ".simulation")

load(file.path(report_path, "results.rdata"))
```

class: center, middle, title-slide

<span style = 'font-size: 200%;'>R로 package 만들어서 Simulation</span>

<br>
<br>

`r Sys.Date()`

<br>
<br>

Sooyong Lee<br><br><span style = 'font-size: 100%;'>Educational Psychology<br><br>The University of Texas at Austin</span>

---

# Find me at...
All the details...

---
class: center, middle


# Slide with centered content in the middle
My name is Alison. I like hot toddies, `#rdogladies`, and babies.

hori:
- left,
- center, 
- right

verti:
- top, 
- middle, 
- bottom

---
class: center, middle 
# Slide with some aligned text
My name is Alison. I like hot toddies, `#rdogladies`,...
.left[and babies.]
---


.pull-left[
...
![a1](http://bit.ly/momtocat)
]
.pull-right[
...
![a1](http://bit.ly/momtocat)
]

---

# Hi there
My name is Alison
--
I like hot toddies
--
`#rdogladies`
--
and babies

---

.pull-left[
```{r plot-last, fig.show = 'hide'}
plot(c(1:10))
```
]
.pull-right[
```{r ref.label = 'plot-last', echo = FALSE}
```
]


---
